---
title: "Challenge 3"
author: "Antonio da Silva"
format: 
  html:
    self-contained: true
editor: visual
execute: 
  echo: true
  message: false
  warning: false
  error: true
---

```{r}
library(tidyverse)
library(here)
library(dplyr)
```

## Summary

```{r}
hiphop <- read_csv(here::here("Week 3", "Lab 3", "hiphop.csv"))

```

```{r}
hiphop1 <- hiphop |>
  mutate(
    age = as.factor(age),
    ethnic = if_else(ethnic == "white", "white", "nonwhite")
)

```

# CHALLENGE

1\.

```{r}
hiphop1 |> 
  select(sex, intl : unclassifiable) |> 
  group_by(sex) |> 
  summarize(across(intl : unclassifiable, mean)) |> 
  pivot_longer(cols = -sex) |> 
  pivot_wider(names_from = sex, values_from = value) |> 
  mutate(Difference = abs(Female - Male))
```

2\.

```{r}
hiphop1 |> 
  select(ethnic, intl : unclassifiable) |> 
  group_by(ethnic) |> 
  summarize(across(intl : unclassifiable, mean)) |> 
  pivot_longer(cols = -ethnic) |> 
  pivot_wider(names_from = ethnic, values_from = value) |> 
  mutate(Difference = abs(nonwhite - white))
```

# **Study Design Critique**

**Based on the design of this study and its context (African American English), what are at least two concerns you have?**

My first concern is that the popular culture questions do not have any substantial proof that it is showing a valid response or answer. This part of the data can easily be skewed by bias. Another concern is that this dataset does not include African American people which purposely exclude a group of people which shows that the dataset does not demonstrate a real life scenario.\
